\section{Spectral Sequence Diagram}
\label{sec:sseq}

\[ \begin{sseq}[xlabelstep=8,ylabelstep=4,entrysize=.3cm]{60}{30}
    \input{ssinstbig.tex}
  \end{sseq}
  \]


We have here the a diagram of the first 60 stems of the $E_2$ page of the Adams Spectral Sequence.
The horizontal axis represents $t-s$ and the vertical axis represents $s$, so a dot in slot $(s,t-s)$ represents a $\F_2$ summand of $E_s^{s,t-s}$.  
The vertical lines represent multiplication (see Theorem~\ref{sec:product}) by $h_0$, which converges to multiplication by 2 in $\pi_*^s$ (see Section \ref{sec:hopfe2} and \ref{sec:HopfInvariant} for a definition of $h_i$); that is, $x$ and $h_0x$ are connected by a vertical line.  
The diagonal lines represent multiplication by $h_1$, the element of the Adams Spectral Sequence detecting the Hopf Fibration.  
A differential, $d_r$, will go 1 square left and $r$ squares up.  
Just from this picture and the Leibniz Rule, we can reason that all differentials before $t-s=13$ are zero, as mentioned in Section \label{sec:pairing}.

One is forced to notice an imperfect pattern when staring at this picture.  
The patterns in the dots seem to have a mod-8 periodicity  towards the top of the diagram.
This is very deep and consequence of the so-called $J$-homomorphism and Bott Periodicity.  
Indeed, the three dots in the ``triangles'' at the top of the diagram ending when $t-s\equiv 3$ (mod 8) are exactly the image of $J$.
The long vertical ``towers'' when $t-s\equiv 7$ (mod 8) are also the image of the $J$ in those dimensions, and these converge to large cyclic summands of $\pi_*^s$, in part explaining the apparent jump in the size of $\pi_i^s$ when $i\equiv 7$ (mod 8).  
The reader is referred to \cite{RavenelGreen} and \cite{imJ}.   


