

\section{Homological Algebra and Steenrod Operations}

\subsection{Tensor and Yoneda Products in Ext}
\label{sec:ExtStructure}

The $\Ext$ functors have quite a bit of structure, which we will discuss briefly in this section.  A fuller treatment can be found in \cite{cartan}.
Fix some field $k$. 
Let $A$ be a $k$-algebra and $X$,$Y$, $Z$ and $W$ be $A$-modules.
Then there is a product, which we will call the tensor product, 
\[\Ext^s_A(X,Z)\otimes \Ext^t_A(Y,W)\to \Ext^{s+t}_{A\otimes A}(X\otimes Y,Z\otimes W)\]

To construct the product, let $K$ be an  $A$-resolution of $X$ and $L$ be an  $A$-resolution of $Y$.  
Then $K\otimes L$ is an $A\otimes A$-resolution of $X\otimes Y$.  
If $[x],[y]$ are cocycles in $\Ext^s_A(X,Z)$ and $\Ext^t_A(Y,W)$ respectively, then consider
\[x\otimes y : K\otimes L \to Z\otimes W\]
This is clearly a cocycle, so represents a class in $\Ext^{s+t}_{A\otimes A}(X\otimes Y,Z\otimes W)$, and the class represented depends only in $[x]$ and $[y]$, not on choice of representatives. If $A$ is a Hopf algebra, there is a map $A\to A\otimes A$, making $X\otimes Y$ an $A$-resolution.  In this case, this tensor product becomes
\[\Ext^s_A(X,Z)\otimes \Ext^t_A(Y,W)\to \Ext^{s+t}_{A}(X\otimes Y,Z\otimes W)\]
In the case that $X$ is a co-algebra, we can pull back by the co-multiplication, and in the case that $Y$ is an algebra, we can compose with the multiplication, yielding.  
\[\Ext^s_A(X,Y)\otimes \Ext^t_A(X,Y)\to \Ext^{s+t}_{A}(X,Y)\]
These are sometimes referred to as cup products.  

We also have Yoneda products in Ext, which are often much easier to compute because you do not need to construct the resolution $K\otimes L$.  
The Yoneda product is a map
\[\Ext^s_A(X,Y)\otimes \Ext^t_A(Y,Z)\to \Ext^{s+t}_{A\otimes A}(X,Z)\]
extending the composition product
\[\Hom_A(X,Y)\otimes \Hom_A(Y,Z)\to \Hom_{A\otimes A}(X,Z)\]
It is computed by considering $\Ext^s_A(X,Y)$ as homotopy classes of degree $s$ chain-maps between resolutions $K\to X$ and $L\to Y$.  
This can be done by the comparison theorem for projective resolutions.  
Since a cocycle in $\Ext^s_A(X,Y)$ is represented by a map $K_s\to Y$, we can extend that map to a chain map with component maps $K_{s+i}\to L_i$, and this is unique up to homotopy.  
Likewise, given a degree $s$ chain map $x$ between resolutions $K$ and $L$, taking the map from $K_s\to L_0\to Y$ gives a chain $x_0$.  Since $x_0d=d_{-1}x=0$, $x_0$ is a cocycle, so indeed Ext is in bijection with homotopy classes of chain maps.  
But chain maps can be composed yielding the desired map.
In particular, this means $\Ext_A(X,X)$ is a ring and $\Ext_A(X,M)$ is a left module and $\Ext_A(M,X)$ is a right module.  



\subsection{Chain Level Construction of Steenrod Operations}
\label{sec:SteenrodConstruction}

This construction is found most clearly in \cite{kahnCupi}, but also in \cite{milgramGroupReps} and \cite{H00RingSpectra}.  

\begin{Theorem}
  Let $A$ be a cocommutative $\F_2$-Hopf Algebra, $X$ an algebra over $A$ and $Y$ a coalgebra over $A$.  
  Then there is a map of graded modules
  \[\A\otimes \Ext_A(Y,X)\to \Ext_A(Y,X)\]
\end{Theorem}

\begin{proof}
  Let $K$ be a projective resolution of $Y$.
  We can view $K\otimes K$ as an $A$-module via the Hopf-comultiplication $A\to A\otimes A$ and a resolution of $Y\otimes Y$.  
  We have an $\A$-map 
  \[\Delta_0:K\to K\otimes K\]
  lifting the comultiplication $Y\to Y\otimes Y$, and this is good for computing cup products. 
  Let $\rho$ be the switching map on $K\otimes K$, that is
  \[\rho (x\otimes y) = y\otimes x\]
  We have
  \[\rho\Delta_0 : K\to K\otimes K\]
  is another map lifting the comultiplication, and thus $rho\Delta_0$ is homotopic to $\Delta_0$.  
  Because $K$ has a contracting homotopy since it is a resolution, we can compute $\Delta_1$ which satisfies
  \[\Delta_1\partial + \partial\Delta_1 = \rho\Delta_0+\Delta_0\]
  Likewise, $\Delta_1$ and $\rho\Delta_1$ are homotopic, and so on, so we can find chain of degree $n$
  \[\Delta_n :K\to K\otimes K\]
  \[\Delta_n\partial + \partial\Delta_n = \rho\Delta_{n-1}+\Delta_{n-1}\]
  Letting $\sigma$ be our contracting homotopy on $K\otimes K\to Y\otimes Y$, we can write an explicit recursive formula
  \[\Delta_n = \sigma(\partial\Delta_n + \rho\Delta_{n-1}+\Delta_{n-1})\]
  
  Finally, define for $[u]\in \Ext_A^{s,t-s}(\F_2,M)$
  \[Sq^i(u)(\sigma) = (u\otimes u)(\Delta_{2s-i}\sigma)\]

  Once can check that these operation obey the Cartan formula and Adem relations, as in \cite{May_ageneral}.  
  
\end{proof}



