\section{Setting up the Adams Spectral Sequence}

The Adams Spectral Sequence is a rather heavy-duty machine for computing $2$-component of the homotopy groups $[Y,X]_*$ for spectra $X$ and $Y$.  
If $Y=S$ and $X$ is a suspension spectrum, this is the 2-component of the stable homotopy groups $\pi^s_*(X)$, which, if you'd like, can be written $\pi^s(X)\otimes \Z_2$, where $\Z_2$ is the 2-adic integers.  
While this is twice removed from the original goal of computing $\pi_*(X)$, at least in this case we have a fighting chance at doing the computations.
Since there are $p$-component analogues, these methods can be combined to compute all of $\pi_*^s(X)$.  
However, as we are about to find, even once the Adam's Spectral Sequence is set up, actually using it is still not easy.  

Morally, the Adams Spectral Sequence works as follows.  
We start with a ``geometric'' resolution of the space $X$
\[X\to K_1\to K_2\to K_3\to ...\]
such that each $K_i$ is a wedge sum of Eilenberg-Maclane spaces and the sequence induced in mod-2 cohomology is exact.  
Thus we get an $\A$-free resolution of $H^*(Y)$, and we consider 
\[[Y,X]\from [Y,K_1]\from [Y,K_2]\from ...\]
Since $K_i$ is a wedge sum of $H\F_2$, we have, for $H^*$ being mod-2 cohomology,
\[[Y,K_i]\cong \bigoplus_i [Y,H\F_2]\cong \bigoplus_i H^*(Y) \cong \bigoplus_i \Hom_\A(\A,H^*(Y))\cong \Hom_\A(H^*(K_i),H^*(Y))\]
One reason we needed to develop spectra is now clear: A space $X$ cannot have $\A$-free cohomology.  
We can take homology of this chain complex and get $\Ext _\A(H^*(X),H^*(Y))$, the starting point or so-called ``$E_2$'' term of the Adams Spectral Sequence.  
We will show this is a sort of over-approximation of $[Y,X]_*\otimes \Z_2$, and the Adams Spectral Sequence ``converges'' to this.  
In the literature of spectral sequences, one might write
\[\Ext_\A(H^*(X),H^*(Y))\implies [Y,X]\otimes \Z_2\]
Computing this Ext group can often be tough, but is algebraic in nature and usually more-or-less mechanical.  
However, we are not done yet.  


The second step in running the Adams Spectral Sequence is to figure out exactly how the convergence works.
When we construct $\Ext_\A(H^*(X),H^*(Y))$, we construct in it a way such that it is still a chain complex.
Thus we can take homology and get what we call the $E_3$ page.
Some elements of $E_2$ will not be cycles, and thus will disappear forever.  
Others will be related by boundaries and become equal.  
Thus $E_3$ is a sub-quotient of $E_2$, just as $E_2$ is a sub-quotient of $\Hom_\A(H^*(X),H^*(Y))$.  
We can continue this process until all the differentials become zero, which we call $E_\infty$.  
It can be shown that, under certain hypothesis, the process does stabilize and the final answer, $[Y,X]\otimes \Z_2$, can be read off the $E_\infty$ page. 
However, computing the differentials on each $E_r$ is notoriously difficult, in fact, it will be the goal of most of the rest of this paper.  
The differential computations are often geometric in nature.  This is not surprising since the algebra of Ext cannot possibly be enough to determine all the homotopy groups.  

\subsection{The Adams Resolution}

\begin{Def}
  We say that a spectrum is ``connective'' if the dimensions in which $H^i$ is nonzero is bounded below.  We say that a spectrum is of ``finite type'' if it has only finitely many cells in each dimension.  
\end{Def}
Let $X$ and $Y$ be spectra, and let $X$ be connective and of finite type, and let $H^*(?)=(H\F_2)^*(?)$ be mod-2 cohomology.  
We want to start by creating the geometric resolution of $Y$ described above.  
We construct the spaces of the resolution as follows.  
Consider $H^*(X)$, and which is finitely generated over $\A$.  
Call those generators $u_i\in [X,H\F_2]_{n_i}$.
We can then form 
\[\bigvee_i u_i:X\to \bigvee_i \Sigma^{n_i}H\F_2\] 
to be a degree 0 map to a wedge sum of suspensions of Eilenberg-Maclane spaces.  
Call the codomain above $K_0$.  
We can then take the fiber of this map and call it $X_1$.  
Repeating this process, we get the following diagram. 

\begin{diagram}
  X & \lTo & X_1 & \lTo & X_2 & \lTo & X_3 & \lTo &...\\ 
  \dTo & & \dTo && \dTo && \dTo\\
  K_0 && K_1 && K_2 && K_3
\end{diagram}

This is one specific construction of the following definition:
\begin{Def}
    An Adams Complex of a spectrum $X$ is a diagram, as above, where $K_0$ is a wedge sum of suspensions of $H\F_2$'s, $X_{i+1}$ is the fiber of $X_i\to K_i$.   

    An Adams Resolution of a spectrum $X$ is an Adams Complex of $X$ with $X_{i}\to K_i$ inducing a surjection in cohomology.  
\end{Def}


Consider an Adams Resolution of $X$.  
Now, notice that the fiber of $X_i \to X_{i-1}$ is $\Sigma^{-1}K_{i-1}$.  
Thus we get a diagram of spectra
\begin{diagram}
  X & \rTo&  K_0 & &\rTo && \Sigma K_1 && \rTo && \Sigma^2 K_2 && \rTo && \Sigma^3 K_3 && \rTo &...\\
    &   &  &    \rdTo  & & \ruTo && \rdTo && \ruTo&& \rdTo && \ruTo\\
    &      &  &   &  \Sigma X_1 & &&& \Sigma^2 X_2 & &&& \Sigma^3 X_3
\end{diagram}

In cohomology we get:

\begin{diagram}
  H^*X & \lTo&  H^*K_0 & &\lTo && H^*\Sigma K_1 && \lTo && H^*\Sigma^2 K_2 && \lTo && H^*\Sigma^3 K_3 && \lTo &...\\
    &   &  &    \luTo  & & \ldTo && \luTo && \ldTo&& \luTo && \ldTo\\
    &      &  &   &  H^*\Sigma X_1 & &&& H^*\Sigma^2 X_2 & &&& H^*\Sigma^3 X_3
\end{diagram}

By exactness of 
\[H^*\Sigma^i X_i\to H^*\Sigma^{i-1}K_{i-1}\to H^*\Sigma^{i-1}X_{i-1}\]
this gives an $\A$-free resolution of $H^*(X)$.  

(Notice that if this was just a complex, the sequence of maps in cohomology would still be a complex).   

Next, we construct what is known in the world of spectral sequences as an ``exact couple''.  
Let $Y$ be a spectra and 
\[E_1^{s,t}=[Y,K_s]_t\]
\[E_1=\bigoplus_{s,t} E_1^{s,t}\]
and
\[A_1^{s,t}=\bigoplus [Y,X_i]_t\]
\[A_1=\bigoplus_{s,t} A_1^{s,t}\]
We call $s$ the filtration level, $t$ the internal degree and $t-s$ the toplogical degree.  

Consider the cofibration sequence
\[X_{i+1}\xrightarrow{i} X_i\xrightarrow{p} K_i\xrightarrow{\partial} \Sigma X_{i+1}\]

This induces a diagram
\begin{diagram}
  A_1 & &\rTo^{i_1} & & A_1 \\
  &\luTo^{\partial_1} & & \ldTo^{p_1}\\
  && E_1
\end{diagram}
which is exact at each node.  

Now, consider
\[d_1=\partial_1p_1\]
and note that this is a differential on $E_1$ since $d_1^2=\partial_1(p_1\partial_1)p_1=0$.  
Thus, we can let $E_2$ be the cohomology of $(E_1,d_1)$ and $A_2$ be the image of $i_1$.  
Let $i_2$ be the restriction, $\partial_2$ be the quotient of $\partial_1$ and define $p_2$ to the image of $i_1$, $p_2$ defined by 
\[p_2(ia)=[p_1(a)]\]
It is an easy exercise to check that this all makes sense, is well defined and that the diagram
\begin{diagram}
  A_2 & &\rTo^{i_2} & & A_2 \\
  &\luTo^{\partial_2} & & \ldTo^{p_2}\\
  && E_2
\end{diagram}
is exact at each point.  This is done in, for instance \cite[Ch~1]{HatcherSS}.

Thus we can iterate this construction and get a sequence of modules $E_r$ and $A_r$ (when $X$ and $Y$ are ambiguous, we write $E_r(Y,X)$ and $A_r(Y,X)$)
\begin{Def}
  We call the sequence of bigraded groups $E_r$ the Adams Spectral Sequence
\end{Def}
We will see later that the limit, which we call $E_\infty$, is closely related to $[Y,X]\otimes \Z_2$


This construction, at first, can be rather disorienting.  
The issue is that $E_{r+1}$ is a sub-quotient (a quotient of a subgroup) of $E_r$.
That means when going from $E_r$ to $E_{r+1}$, some elements will become equal to others, while some elements will cease to exist.
If $x\in E_r$ has $d_r(x)=0$, then $x$ has some image in $E_{r+1}$, so we say that $x$ survives to the $r+1$ page, and we use the same symbol to denote it on the $E_{r+1}$ page.  
This is not as confusing as it might sound, because geometrically $x$ is represented by the same map on the $E_r$ page and the $E_{r+1}$ page.  
If $d_r(x)\ne 0$, we say the differential kills $x$.  
Notice that we say the $x$ survives even if there is some other element $y$ with $d_r(y)=x$, that is, even if $x$ is a boundary and the image of $x=0$ in $E_{r+1}$.


We recall
\[E_1^{s,t}=[Y,K_s]_t\cong \Hom_\A^t(H^*(K_s),H^*(Y))\]
where $\Hom^t$ means maps of graded groups lowering degree by $t$ and where the second equivalence comes from the argument in the introduction.  
Since the $H^*(K_s)$ make an $\A$-free resolution of $H^*(X)$, we have
\[E_2^{s,t}=\Hom_\A^{s,t}(H^*(X),H^*(Y))\]


Let us unravel what this sequence means.  
Our exact couple unravels into the following diagram where the ``staircases'' are exact.
\begin{RefDiagram}
  \begin{diagram}
    \vdots &&&& \vdots  &&&& \vdots \\
    \dTo & &&& \dTo  & &&& \dTo &&& &  \\
    [Y,X_s]_{t-s+1} & \rTo & [Y,K_{s}]_{t-s+1} & \rTo & [Y,X_{s+1}]_{t-s} & \rTo & [Y,K_{s+1}]_{t-s} & \rTo & [Y,X_{s+2}]_{t-s-1}\\
    \dTo & &&& \dTo  & &&& \dTo &&& &  \\
    [Y,X_{s-1}]_{t-s+1} & \rTo & [Y,K_{s-1}]_{t-s+1} & \rTo & [Y,X_{s}]_{t-s} & \rTo & [Y,K_{s}]_{t-s} & \rTo & [Y,X_{s+1}]_{t-s-1}\\
    \dTo & &&& \dTo  & &&& \dTo &&& &  \\
    [Y,X_{s-2}]_{t-s+1} & \rTo & [Y,K_{s-2}]_{t-s+1} & \rTo & [Y,X_{s-1}]_{t-s} & \rTo & [Y,K_{s-1}]_{t-s} & \rTo & [Y,X_{s}]_{t-s-1}\\
    \dTo & &&& \dTo  & &&& \dTo &&& &  \\
    \vdots &&&& \vdots  &&&& \vdots 
  \end{diagram}
  \label{sec:exactCouple}  
\end{RefDiagram}

How do we calculate the differentials?
Put your pencil on the module in the center row: $[Y,K_{s-1}]_{t-s+1}$.
Pretend your pencil tip is $x\in[Y,K_{s-1}]_{t-s+1}$.
By definition, the map $d_1$ is obtained by going straight across.  
If $d_1(x)=0$, then $x$ represents an element in $E_2$ and so $d_2$ is expected to be defined.  
To calculate $d_2$, move your pencil to $\partial_1(x)\in [Y,X_s]_{t-s}$.  
By exactness, since $x$ is zero in $[Y,K_s]_{t-s}$, there is a preimage of $x$ above in $[Y,X_{s+1}]_{t-s}$.  
Applying $p_1$ to this will give an element of $[Y,K_{s+1}]_{t-s}$, and this is $d_2([x])$.  
In general, a differential is calculated by pushing $\partial_1(x)$ ``up'' as far as you can before applying $p_1$.  

For spheres, we can do a bit better.  
Exactly like with spaces (you should check this), there is a relative homotopy group
\[\pi_i(A,X)=[(D,S^{-1}),(X,A)]_i\]
where $D=\Sigma^\infty D^0$ and the homotopies are to leave the boundary of $D$ in $A$.  
Rewriting our diagram like this for $Y=S$, we have

\begin{diagram}
  \vdots &&&& \vdots  &&&& \vdots \\
  \dTo & &&& \dTo  & &&& \dTo &&& &  \\
  \pi_{t-s+1}X_s & \rTo & \pi_{t-s+1}(X_s,X_{s+1}) & \rTo & \pi_{t-s}X_{s+1} & \rTo & \pi_{t-s}(X_{s+1},X_{s+2}) & \rTo & \pi_{t-s-1}X_{s+2}\\
  \dTo & &&& \dTo  & &&& \dTo &&& &  \\
  \pi_{t-s+1}X_{s-1} & \rTo & \pi_{t-s+1}(X_{s-1},X_{s}) & \rTo & \pi_{t-s}X_{s} & \rTo & \pi_{t-s}(X_{s},X_{s+1}) & \rTo & \pi_{t-s-1}X_{s+1}\\
  \dTo & &&& \dTo  & &&& \dTo &&& &  \\
  \pi_{t-s+1}X_{s-2} & \rTo & \pi_{t-s+1}(X_{s-2},X_{s-1}) & \rTo & \pi_{t-s}X_{s-1} & \rTo & \pi_{t-s}(X_{s-1},X_{s}) & \rTo & \pi_{t-s-1}X_{s}\\
  \dTo & &&& \dTo  & &&& \dTo &&& &  \\
  \vdots &&&& \vdots  &&&& \vdots 
\end{diagram}

You can, without loss of generality (using a mapping-cylinder construction) assume all the maps $X_i\to X_{i-1}$ are inclusions of subcomplexes, although the only difference this makes is to allow you to use language as if $X_i\subset X_{i-1}$.  
Thus, let
\[f:(D^{t-s+1},S^{t-s})\to (X_s,X_{s+1})\]
be an element of $\pi_{t-s+1}(X_{s-1},X_{s})$.  
Then $\partial_1(f)$ is the boundary of $f$, that is, $f|_{S^{t-s}}$.  
The image of $\partial_1(f)$ is in $X_{s}$, but you may be able to find a homotopy compressing the image to $X_{s+r-1}$.
Thus $d_r(f)$ is the inclusion of this map into $\pi_{t-s}(X_{s+r-1},X_{s+r})$.  
This is the strategy we will use to compute the vast majority of the differentials.  

\subsection{Convergence of the Adams Spectral Sequence}

Before we go any further in discussing how to calculate $E_\infty$, let us prove the following result
\begin{Theorem}
  \label{sec:converge}
  Use the notation of above.  Let 
  \[F^{s,t}=\im\left([Y,X_s]_{t-s}\to [Y,X]_{t-s}\right)\]
  Then 
  \[\bigcap_n F^{s+n,t+n}=\Torsion_{p>2}[Y,X]_{t-s}\]
  where $\Torsion_{p>2}$ means the set of all elements annihilated by a power of an odd prime.  
  Finally, for each $(s,t)$ there is an $R$ such that for all $r\ge R$
  \[E_r^{s,t}=\frac{F^{s,t}}{F^{s+1,t+1}}\]
  We call such $E_r^{s,t}$ by $E_\infty^{s,t}$.  
  We can write this compactly as
  \[E_2=\Ext^{s,t}_\A(H^*(X),H^*(Y))\implies [Y,X]_{t-s}\otimes \Z_2\]
\end{Theorem}



We need a lemma to prove the rest.  
First of all.
\begin{Lemma}
  \label{sec:compth}
  Adams Resolutions are ``comparable'', that is, given spectra $X$ and $Y$, $f:X\to Y$ and Adams Resolutions $X_i$ and a complex $Y_i$, you can find $f_i:X_i\to Y_i$ making the following diagram commutative up to homotopy
  \begin{diagram}
    X & \lTo & X_1 & \lTo & X_2 & \lTo & ...\\
    \dTo^f & & \dTo^{f_1} && \dTo^{f_2}\\
    Y & \lTo & Y_1 & \lTo & Y_2 & \lTo & ...
  \end{diagram}
\end{Lemma}

\begin{proof}
  Let $K_i$ be the cofiber of $X_{i+1}\to X_i$, $L_i$ the cofiber of $Y_{i+1}\to Y_i$, and recall that the suspensions of the $K_i$ and $L_i$ give free resolutions of $X$ and $Y$ in cohomology.  
By Theorem \ref{sec:compth} for cohomology, we can find $\hat{f}^*_i$ in cohomology such that the following diagram commutes
  \begin{diagram}
    H^*X & \lTo & H^*K_0 & \lTo & H^*\Sigma K_1 & \lTo & ...\\
    \uTo^{f^*} & & \uTo^{\hat{f}^*_1} && \uTo^{\hat{f}^*_2}\\
    H^*Y & \lTo & H^*L_0 & \lTo & H^*\Sigma L_1 & \lTo & ...
  \end{diagram}
But recall that that
\[[?,K_i]\cong \Hom_\A(H^*(K_i),H^*(?))\]
And thus $\hat{f}^*_i$ is induced by $\hat{f}_i:K_i\to L_i$.  
But $K_i$, $K_{i+1}$ and $X_i$ form one distinguished triangle, $L_i$, $L_{i+1}$ and $Y_i$ form another, and we have maps from the $K$'s to the $L$'s, so we automatically get a map $f_i:X_i\to Y_i$ so that everything commutes. 
\end{proof}

The proof from here on out will proceed much like in \cite[Ch~2]{HatcherSS}.

\begin{proof}[Proof of \ref{sec:converge}:]

Now, let us focus our attention on $\bigcap_i F^{s+i,t+i}$.  
Recall from Diagram \ref{sec:exactCouple} that $[Y,K_i]_{l}$ is a $\F_2$ vector space, and thus it has no odd prime torsion.
The staircase is exact, so the vertical maps must be isomorphisms on the odd prime torsion. 
Thus the odd prime torsion in $[X,Y]_{t-s}$ is passed all the way down from $[Y,X_s]_{t-s}$ to $[Y,X]_{t-s}$ and so $F^{s,t}$ contains it for each $(s,t)$.

For the other direction, pick some integer $k$.  
Since $[X,X]$ is an abelian group, we can take the identity map and multiply it by $2^k$, which as a map we will denote ($*2^k$).
Let $Q$ be the cofiber of this map, so that we have the long exact sequence
\[...\to [Y,X]_i\xrightarrow{(*2^k)_*} [Y,X]_i \to [Y,Q]_i\to ...\]
and note by exactness that the image of the map $[Y,Q]_i\to [Y,X]_{i-1}$ is all $2$-torsion, as is the kernel of $[Y,X]_i\to [Y,Q]_i$.  Thus $[Y,Q]_i$ is all 2-torsion.
If $\alpha\in [Y,X]_i$ is either odd prime torsion or non-torsion, then our connective and finite-type hypothesis implies $[Y,X]_i$ is finitely generated, so there is a $k$ such that $\alpha$ is not divisible by $2^k$.  
Thus $\alpha$ is not in the image of $(*2^k)$, and so has nonzero image in $[Y,Q]_i$.  
By Theorem \ref{sec:compth}, if $\alpha$ has a preimage in $[Y,X_j]_i$ for all $j$, then the image of $\alpha$ in $[Y,Q]_i$ will have a similar property for the Adams resolution of $Q$.  
Thus it is sufficient to prove that if $[Y,X]_i$ is all 2-torsion then the Adams resolution eventually has $[Y,X]_i=0$.  

To show this, assume $X=Z_0$ is all 2-torsion.
Note that all the $[Y,X]_i$ are finite.  
We inductively build an Adams Complex
\begin{diagram}
  Z_0 & \lTo & Z_1 & \lTo & Z_2 & \lTo & Z_3 & \lTo &...\\ 
  \dTo & & \dTo && \dTo && \dTo\\
  L_0 && L_1 && L_2 && L_3
\end{diagram}
let $n_i$ be the smallest number with $[Y,Z_i]_{n_i}\ne 0$, and let $L_i$ be a wedge sum of $H\F_2$ on a basis for $H^{n_i}(Z_i)$.  
Let the map from $X_i\to L_i$ be the obvious one and let $Z_{i+1}$ be the cofiber.  
Notice that in $H^{n_i}$ the map $Z_i\to L_i$ is an isomorphism, so also in $H_{n_i}$, so in $[Y,?]_k$ for $k< n_i$ it is an isomorphism and we have
\[[Y,L_i]_{n_i}=[Y,Z_i]_{n_i}\otimes \Z_2\]
This is a surjection, so by the cofiber sequence we have for $k<n_i$ the group $[Y,Z_{i+1}]_k=0$ and $[Y,Z_{i+1}]_{n_i}$ is smaller than $[Y,Z_{i}]_{n_i}$.  
Since these groups are finite, we must eventually get $[Y,Z_{i+1}]_{n_i}=0$.  
This means for each $i$, there is an $n$ such that $[Y,Z_{i+1}]_i=0$ for $i\ge n$.  
Applying Theorem \ref{sec:compth} over the identity map $X\to X$, 
we find if any element in $[Y,X]_{t-s}$ has preimage in $[Y,X_s]_{t-s}$ for all $s$ (recall to make this sequence we take suspensions, which is equivalent to a grading shift), that element would have nonzero image in $[Y,Z_s]_{t-s}$ for all $s$, which we just said is impossible.  
Thus the intersection of the $F^{s+n,t+n}$ must be only odd prime torsion.  


We can finally prove the convergence result.
Recall that $A_r^{s,t}$ is all the elements of $[Y,X_s]_{t-s}$ with vertical preimages in $[Y,X_{s+r}]_{t-s}$.  
By that which has been proved thus far, for sufficiently large $r$ this contains no 2-torsion.  
Also, the map $A_r^{s,t}\to A_r^{s-1,t-1}$ is an isomorphism on the non torsion and odd prime torsion, so this map is injective.
Thus, recalling the definition of the differential $d_r$, since the map $E_r^{s,t}\to A_r^{s,t}$ is zero by exactness of the staircase, for large $r$ the differentials originating at $E_r^{s,t}$ are zero.
Also for large enough $r$ there are no differentials into $E_r^{s,t}$, since such differentials would come from $E_r^{s-r,t-r-1}$, which is nothing for $r>s$.  
Thus for all $r$ greater than some $R$, we have that projection gives an isomorphism $E_r^{s,t}\to E_{r+1}^{s,t}$.
Notice that, in fact, $E_\infty^{s,t}$, by exactness of the staircase, is isomorphic to the cokernel of the previous vertical maps, which for large $r$ is exactly the inclusion $F^{s+1,t+1}\to F^{s,t}$, which is the theorem.  

\end{proof}

Given an actual homotopy class, we can tell what filtration it will be detected in in the Adams Spectral Sequence.  Notice that if $f\in [Y,X]_*$ is detected by an element in filtration $s$, we can factor it as the composite of $s$ maps which induce 0 in cohomology.  
To see this, see that $f$ is detected by a map $[Y,K_s]_*$, which can be pushed to a map $[Y,X_s]_*$ which is a lift of $f$.  
Thus $f$ factors as the $s-1$ maps in $[X_{l}, X_{l-1}]_*$ for $l<s$ (these are 0 in cohomology) and the composite of $Y\to X_s\to X_{s-1}$.
We state this easy fact as a lemma.
\begin{Lemma}
  \label{sec:filtlemma}
  If $f\in [Y,X]_*$ is detected by an element in filtration $s$, then it can factor as the composite of $s$ maps, each of which induce the zero map in cohomology.
\end{Lemma}





\subsubsection{Some Remarks}

There are a few ways to generalize this process or just make it a bit nicer.
First of all, we can use homology instead of cohomology.  
The difference here is that we end up using smash products instead of wedge products of $H\F_2$, but in the end we get a spectral sequence
\[E_2 = \Ext_{\A_*}(H_*(Y),H_*(X))\implies [Y,X]\otimes \Z_2\]
where the $\implies$ symbol means that there is an $E_\infty$ page and it is isomorphic successive quotients of the right hand of the $\implies$ arrow, and
\[\A_*=\Hom_{\F_2}(\A,\F_2)=(H\F_2)_*(H\F_2)\]
We can also replace $H\F_2$ with any generalized cohomology theory $E$, like cohomology mod odd primes, 
your favorite flavor of K-Theory (for instance $E=BU,BO,KO$) or cobordism ($E=MU,MSU,BP$).  
The zoo of spectra and cohomology theories are discussed in great detail in Ravenel's famous ``Green Book'' \cite{RavenelGreen}.
In this case, under certain hypothesis about $E,X$ and $Y$, we have
\[E_2 = \Ext_{E_*E}(E_*(Y),E_*(X))\implies [Y,X]^{E}\]
where $[Y,X]^{E}$ is, roughly, maps $f$ whose equivalence is detected by the induced map $E_*(f)$.  
More details on this can be found in, for instance \cite{RavenelGreen}, \cite[Ch~IV]{H00RingSpectra}.  
When $E=BP$, the spectral sequence is has many many fewer nonzero differentials, and earns the name ``Adams-Novikov Spectral Sequence''.  

The reader is invited to look at Appendix \ref{sec:sseq} at this point, containing a diagram of the $E_2$ page of the Adams Spectral Sequence for Spheres.  

\subsection{Hopf Invariant One Maps in $\Ext_\A(\F_2,\F_2)$}

\label{sec:hopfe2}

Let $f\in \pi_{4n-1}(S^{2n})$ have odd Hopf Invariant.  
Since the group $\pi_{4n}(S^{2n+1})$ is stable, there is an $\hat{f}=\Sigma f\in\pi_{2n-1}^s(S)$ coming from $f$.  
Notice that $\hat{f}\ne 0$, since the Steenrod Squares commute with suspensions, so in the cohomology ring of $S^{2n+1}\cup_{\Sigma f} D^{4n+1}$, the Steenrod Square $Sq^{2n}$ is not zero.  
You might notice that in $S^{2n+1}\cup_{g} D^{4n+1}$ for some $g\in \pi_{4n}(S^{2n+1})$, we know that the cup product square on the $2n+1$ cohomology class is zero.
However, we can still apply $Sq^{2n}$ and ask if it is zero or not.  
If $g$ is the suspension of a map with a Hopf invariant, this will detect the parity of the Hopf Invariant.
Since Hopf Invariant is a homomorphism and nullhomotpic maps have Hopf Invariant zero, we know that $\Sigma f$ has even order.  
This means that $\hat{f}$ is detected by an element in the Adams Spectral Sequence.  


We can do better however.  We are able to say exactly what elements of $\Ext_\A(\F_2,\F_2)$ correspond to possible maps of Hopf Invariant One.  
We need the following lemma
\begin{Lemma}
  Suppose that $\hat{f}:S^{2n-1}\to S$ comes from an element of odd Hopf Invariant.  
  Suppose there is a spectrum $X$ such that the following diagram commutes
  \begin{diagram}
    S^{2n-1} & \rTo^{f_1} & X\\
             & \rdTo_{\hat{f}} & \dTo^{f_2}\\
             &            &   S
  \end{diagram}
  Then either $f_1^*$ or $f^*_2$ is nonzero.
\end{Lemma}

\begin{proof}
  Suppose both maps are zero in cohomology.  
  We have the following diagram of spectra
  \begin{diagram}
      &            & S^{2n-1}\\
      &            & \dTo^{f_1}\\
    S & \lTo^{f_2} & X \\
    \dTo &  & \dTo^j\\
    S\cup_{\hat{f}} D^{2n} & \lTo^i & X\cup_{f_1} D^{2n}\\
    \dTo & & \dTo\\
    S^{2n} & \lEq & S^{2n}
  \end{diagram}
where the two columns are cofibrations sequences.  
Applying cohomology, we have that the two columns are exact.  
In fact, since $f_1^*=0$, the right column is short-exact.  
  \begin{diagram}
    \F_2 & \rTo^{0} & H^*X\\
    \uTo &  & \uOnto_{j^*}\\
    \F_2\oplus \Sigma^{2n}\F_2 & \rTo^{i^*} & H^*(X\cup_{f_1} D^{2n})\\
    \uTo & & \uInto\\
    \Sigma^{2n}\F_2 & \lEq & \Sigma^{2n}\F_2\\
  \end{diagram}
  Let $\alpha$ be the generator of $H^0( S\cup_{\hat{f}} D^{2n})$ and $\beta$ be the generator of $H^{2n}( S\cup_{\hat{f}} D^{2n})$.  
  Since we know $\beta$ has a preimage in $H^*(S^{2n})$ and since the bottom right vertical map is an injection (by exactness), $i^*\beta$ generate the kernel of $j^*$ and is nonzero.  
  But $\beta=Sq^{2n}\alpha$, so $Sq^{2n}i^*\alpha=i^*\beta$, so $i^*\alpha\ne 0$ and thus is not in the kernel of $j^*$.  
  This means $j^*i^*\alpha\ne 0$.  But by commutativity of the square, it should be, so we get a contradiction.  
\end{proof}

\begin{Cor}
  If there is a map of odd Hopf Invariant in $\pi_{4n-1}(S^{2n})$, there is an element of $\Ext^{1,2n}_\A(\F_2,\F_2)$ which survives to the $E_\infty$ page.  
\end{Cor}
\begin{proof}
  By Lemma \ref{sec:filtlemma}.
\end{proof}


Since the kernel of $\A\to \F_2$ is generated over $\F_2$ by the indecomposable elements, we can conclude that $\Ext^{1,t}(\F_2,\F_2)$ is nonzero when and only when $t$ is a power of 2.  
\begin{Def}
  \label{sec:hidef}
  We will refer to the generator of $\Ext^{1,2^i}(\F_2,\F_2)$ as $h_i$.  
\end{Def}
The element $h_0$ detects twice the identity map in $\pi_0(S)$, $h_1$ detects the Hopf Fibration and $h_2$ and $h_3$ detect similar maps for the Quaternions and Octonions.  


